Lyman-$\alpha$ photons through rotating outflows

### 2018-03-29 paper/paper.tex
edit + fig size

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.90\textwidth]{./figures/results/doppler_shift_logtau6_theta90}
  \end{center}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity viewed perpendicular to the rotation axis}. 
    Here we fix $\tauh=10^6$ and $\theta=90^\circ$.
    We vary \vrot increasing from left to right and \vout increasing from top to
    bottom. 
    The thin black line corresponds to the \lya line obtained with
    CLARA without any rotation and the indicated outflow velocity.
    The thick black line corresponds to the results including both
    outflows and rotation.
    The thick gray line shows the results of modifyin the pure outflow
    solution by the Doppler shift presented in Equation \ref{eq:shift_x}
    (in thin line), if there is a radiative transfer of rotation and outflows
    (thick and clear line), and if there is a radiative transfer of only outflows,
    but also a Doppler shift from the rotational velocity (thick and dark line).
    \label{fig:doppler_shift}}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.90\textwidth]{./figures/results/doppler_shift_logtau6_theta0}
  \end{center}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity viewed parallel to the rotation axis}. 
    Here we fix $\tauh=10^6$ and $\theta=0^\circ$.
    \label{fig:doppler_shift_theta_0}}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout5_logtau5.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout25_logtau5.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout50_logtau5.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout5_logtau6.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout25_logtau6.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout50_logtau6.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout5_logtau7.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout25_logtau7.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout50_logtau7.pdf}
\end{center}
\caption{\textbf{Standard Deviation for RT and DS:} The triangles represent the Radiative
  Transfer and the lines represent the Doppler Shift.
  \label{fig:standard_deviation}}
\end{figure*}

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=0.49\textwidth]{./figures/results/doppler_shift_logtau6_theta90}
  \end{center}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity viewed perpendicular to the rotation axis}. 
    Here we fix $\tauh=10^6$ and $\theta=90^\circ$.
    We vary \vrot increasing from left to right and \vout increasing
    from top to bottom. 
    The thin black line corresponds to the \lya line obtained with
    CLARA without any rotation and the indicated outflow velocity.
    The thick black line corresponds to the results including both
    outflows and rotation.
    The thick gray line shows the results of modifyin the pure outflow
    solution by the Doppler shift presented in Equation \ref{eq:shift_x}
    (in thin line), if there is a radiative transfer of rotation and outflows
    (thick and clear line), and if there is a radiative transfer of
    only outflows, but also a Doppler shift from the rotational
    velocity (thick and dark line).  
    \label{fig:doppler_shift}}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.49\textwidth]{./figures/results/doppler_shift_logtau6_theta0}
  \end{center}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity viewed parallel to the rotation axis}.     
    Same layout as Figure \ref{fig:doppler_shift},
    this time the viewing angle corresponds to $\theta=0^\circ$.
    The effects of rotation on
    the  \lya\ line morphology are not visible when viewed parallel to
    the rotation axis.
    \label{fig:doppler_shift_theta_0}}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_std_vout5_logtau5.pdf}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_std_vout25_logtau5.pdf}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_std_vout50_logtau5.pdf}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_std_vout5_logtau6.pdf}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_std_vout25_logtau6.pdf}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_std_vout50_logtau6.pdf}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_std_vout5_logtau7.pdf}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_std_vout25_logtau7.pdf}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_std_vout50_logtau7.pdf}
\end{center}
\caption{\textbf{Standard Deviation for RT and DS:} The triangles represent the Radiative
  Transfer and the lines represent the Doppler Shift.
  \label{fig:standard_deviation}}
\end{figure*}
